We have explored media synchronization between heterogeneous media components,
and highlighted the need for temporal interoperability on the Web platform.
While internal timing is the popular approach to Web-based media, external
timing is the key to temporal interoperability.

This chapter provided introduction to external timing as well as the media
model and the programming model that follows from this approach. By focusing
on modularity, loose coupling and client-side synthesis, this media model is
well aligned with key design principles of the Web, thereby fully extending
the flexibility and extensibility of the Web platform to timed Web
applications. Equally important, the external timing approach is a gateway to
precise distributed playback and media orchestration, enabling precise timing
and control also in multi-device Web-based media experiences.

To encourage temporal interoperability on the Web platform, the W3C Multi-
device Timing Community Group (MTCG)~\cite{mtcg} advocates standardization of
the timing object~\cite{timingobject} as common interface to external timing
and control. Timingsrc~\cite{timingsrc}, is an open source JavaScript
implementation of the timing object programming model. Using the external
timing approach, we have demonstrated that the Web is already a strong
platform for timed, multi-device media, though it was not designed for it.
With standardization it will become even better, likely unleashing a new wave
of Web-based creativity across a variety of application domains.

Finally, as the external timing approach to media synchronization works on the
Web, it may also be ported to other native applications in the IP environment.
This provides a simple mechanism for making distributed media from a mixture
of native and Web-based media components.
